\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-20 jss/article.tex
small correction

Based on the point and interval estimates, the 31st hospital seems the most reliable one among all the candidates. But when fitting a model it is always a good idea to question how reliable the estimation procedure is. For example, does our procedure generate interval estimates that have good repeated sampling properties? To answer this question the \code{coverage} function generates pseudo-datasets regarding the estimated $r~(=336.37)$ as a given true value. For reference, we can try any other value of $r$, for example $r=200$, by replacing the code below with `\code{R> pcv <- coverage(p, A.or.r = 200, mean.PriorDist = 0.02, nsim = 1000)}.

Then, how reliable are these intervals? Does our procedure generate interval estimates that have good repeated sampling properties? To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=336.37)$ is a true value. We also could try any other value of $r$, for example $r=200$, by adding another argument, \code{A.or.r = 200}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 200, nsim = 1000)}.

>>>>

Based on the point and interval estimates, the 31st hospital seems the most reliable one among all the candidates. But when fitting a model it is always a good idea to question how reliable the estimation procedure is. For example, does our procedure generate interval estimates that have good repeated sampling properties? To answer this question the \code{coverage} function generates pseudo-datasets assuming the estimated $r~(=683.53)$ is a true value. For reference, We also could try any other value of $r$, for example $r=600$, by adding another argument, \code{A.or.r = 600}, into the code below; \code{R> pcv <- coverage(p, A.or.r = 600, nsim = 1000)}.
